The demographic costs of sexually antagonistic selection in partially selfing populations

### 2022-02-08 doc/SA-Hermaphrodites-wDemography-R1.tex
Add Dryad doi, update .gitignore, etc
This commit added the official dryad doi to the references,
added the ./notes/ folder to the list of untracked folders for the
public repo, and made minor edits to the README.md

\textit{Online enhancements}: Dryad digital repository ({\itshape https://datadryad.org/stash/share/81sAuXGEg8cSh-S9VVL0PfBCsl6YLkG1OIFBCvOefac}).

@@

Here, we briefly describe a matrix model incorporating multiple life-cycle stages and a single diallelic locus under SA selection on male and female fertility for populations of partially-selfing simultaneous hermaphrodites. We focus our presentation on a two-stage example of the model and discuss its' underlying biological assumptions. The derivation of the general model for any number of age or stage classes is provided in the Online Supplementary Material. The derivation follows closely the logic presented in \citet{deVriesCaswell2019a, deVriesCaswell2019b}, and in fact, it reduces to the two-sex stage-structured model of \citet{deVriesCaswell2019a} under obligate outcrossing (when selfing is not allowed). All computer code and data necessary to reproduce the results are available on Dryad (\url{https://datadryad.org/stash/share/81sAuXGEg8cSh-S9VVL0PfBCsl6YLkG1OIFBCvOefac}) and on GitHub (\url{https://github.com/colin-olito/SA-Hermaphrodites-wDemography}).

>>>>

\textit{Online enhancements}: Dryad digital repository (\citealt{Olito-DeVries-2022-Dryad}; reviewer link: \url{https://datadryad.org/stash/share/81sAuXGEg8cSh-S9VVL0PfBCsl6YLkG1OIFBCvOefac}).

@@

Here, we briefly describe a matrix model incorporating multiple life-cycle stages and a single diallelic locus under SA selection on male and female fertility for populations of partially-selfing simultaneous hermaphrodites. We focus our presentation on a two-stage example of the model and discuss its' underlying biological assumptions. The derivation of the general model for any number of age or stage classes is provided in the Online Supplementary Material. The derivation follows closely the logic presented in \citet{deVriesCaswell2019a, deVriesCaswell2019b}, and in fact, it reduces to the two-sex stage-structured model of \citet{deVriesCaswell2019a} under obligate outcrossing (when selfing is not allowed). All computer code and data necessary to reproduce the results are available on Dryad (\citealt{Olito-DeVries-2022-Dryad}, reviewer link: \url{https://datadryad.org/stash/share/81sAuXGEg8cSh-S9VVL0PfBCsl6YLkG1OIFBCvOefac}) and on GitHub (\url{https://github.com/colin-olito/SA-Hermaphrodites-wDemography}).
